Detecting Hand Direction for Computer Interaction

### 2014-12-09 paper/paper.tex
Made a few changes to paper.

Created feature vectors to describe image.  We evaluated two different methods of extracting these feature vectors: convolutional neural networks and histograms of gradient orientations.  We then trained regressors from these features to the ground truth location.  We experimented with several different types of regressors and report here the results for least squares linear regression and K-nearest neighbors regression.  Other regression methods did not provide any significant improvement.  We used the scikit-learn library implementation of these methods \cite{scikit-learn}.

@@

\subsection{Classifier}
We experimented with several different classifiers including k-Nearest Neighbors, linear regression, and SVM. We found that a combination of k-nearest neighbors and linear regression worked best across a wide variety of data. We trained the k-nearest neighbors and linear regression models from sci-kit learn separately on 15 sets of test data comprised of the HOG features computed from each image. These models each predicted a location based on HOG input. These locations were averaged together and fed into a smoothing algorithm to compute the final location.

>>>>

To perform the task of deciding where a hand is pointing, we first created feature vectors to describe the images, then we used regression to predict where a hand was pointing.  We evaluated two different methods of extracting these feature vectors: convolutional neural networks and histograms of gradient orientations, which are described in detail below.

@@

\subsection{Classifier}
We experimented with several different regression models including k-Nearest Neighbors, and least squares linear regression. We found that an average of the output of k-nearest neighbors and linear regression worked best across a wide variety of data. We trained the k-nearest neighbors and linear regression models using the scikit-learn library\cite{scikit-learn}.  The models took in the features vectors from HOG and the neural networks and predicted a location. These locations were averaged together and fed into a smoothing algorithm to compute the final location.
